The pollination trade-off

### 2018-03-02 publication/manuscript.Rmd
Small changes to figure legends

```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "Trade off predictions j."}
loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
# loadd(model_correlations)

# p1 <- model_correlations %>%
#   filter(var_trans == "log", 
#          scale == "global") %>%
#   ggplot(aes(x = pearson_slope)) + 
#   geom_vline(xintercept = 0.5, size = 0.25, linetype = 2) +
#   stat_density(trim = F, geom = "line") +
#   pub_theme() +
#   labs(x = "slope\n(heterospecific ~ conspecific pollen gain)")
# 
get_pred_range <- function(x){
  tidied_fixed %>% filter(pollen_category == x, var_trans == "log", scale == "global") %$% estimate %>% range()
}

@@

## Awknowledgements

>>>>

```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "Trade off predictions j."}
loadd(trade_off_predictions, model_linear_fits, tidied_fixed)

get_pred_range <- function(x){
  tidied_fixed %>% 
    filter(pollen_category == x, var_trans == "log", scale == "global") %$% 
    estimate %>% range()
}

@@
